YouTube Kids: The Effect of YouTube on Children’s Racial Learning

### 2025-02-27 manuscript.qmd
updated manuscript draft
manuscript draft updated
knit/rendered manuscripts
Added some informative comments

This study will examine the relationship between YouTube usage and children’s development of racial attitudes, so as to understand whether and the degree to which YouTube may be a site of ethnic-racial socialization where children develop prejudices against those of other races. 
I hypothesize that time spent on YouTube and children’s observation of racial regularities should covary; as children spend more time on YouTube, they may observe more negatively valenced racial regularities including people of color [@guoharlow_2014_usergenerated; @rollinsetal_2022_who]. Thus, I hypothesize that if children spend more time on YouTube, they will display greater racial stereotyping and prejudice against outgroups. While some children may not be consciously aware of on-screen racial regularities, these dynamics may still affect their racial attitudes [@hugheswatford_2022_racial]. As such, I hypothesize that the relationship between children’s time spent on YouTube and their exhibited racial stereotyping and prejudice will be mediated by their observations of negative racial regularities. 
One additional factor that may moderate the relationship between time spent on YouTube and racial attitudes is whether a child’s favorite YouTuber is of a race other than their own, via the parasocial contact hypothesis. This theory suggests that when individuals have limited real life interpersonal contact with minority groups, the formation of parasocial (one-sided) relationships with outgroup media figures may reduce stereotyping and prejudice [@schiappaetal_2005_parasocial; @wongetal_2022_theorizing]. Much of the parasocial contact hypothesis literature explores the prejudice reduction made possible by parasocial relationships with television characters, yet the growing popularity of social media presents another medium through which parasocial relationships may be formed. If positive parasocial contact hypothesis effects may be observed when individuals form relationships with characters in other media, so too should these effects be observed when individuals have parasocial relationships with outgroup influencers [@banasetal_2020_metaanalysis]. Thus, I pose my third hypothesis: the relationship between the amount of time that children spend on YouTube and their racial stereotyping and prejudice will be moderated by whether they have a parasocial relationship with a favorite YouTuber of a race other than their own. Specifically, if children have a favorite YouTuber of a race other than their own and they have a parasocial relationship with this YouTuber, they will display less racial stereotyping and prejudice.

@@

### Participants and Procedures {#sec-participants-and-procedures}
This study will include children between the ages of 8 and 13. Though children may express negative racial attitudes prior to this point in development, during early adolescence, children develop the ability to recognize and reflect on the racial patterns and dynamics present in their environments (Hughes & Watford, 2022). As such, this age range should allow me to observe how the observation racial regularities present on YouTube may affect children’s stereotyping and prejudicial attitudes, and how such a phenomenon develops. Participants will be recruited through Qualtrics Panels, which will allow me to obtain a representative sample of parents and children; other studies have used Qualtrics Panels with similar methods and populations (Byrd & Ahn, 2020). 
Data will be collected during February and March of 2025 from families recruited via Qualtrics Panels. Participating families will receive two Qualtrics surveys to be completed asynchronously, and they will receive compensation (around $10-$15; the final amount will be determined by Qualtrics Panels) after both surveys have been completed. First, parents will complete a demographics and YouTube usage survey, in which they will answer questions related to parent and child demographics (child age, race/ethnicity, parent income and level of education, etc), as well as questions regarding their child’s YouTube usage (for instance, time spent on YouTube, as reported by their child’s device screen time). 
Then, children will complete their own survey.

@@

# In the future, will have a final, written out, intermediate dataset that will be read in here.

@@

>>>>

This study will examine the relationship between YouTube usage and children’s development of racial attitudes, so as to understand whether and the degree to which YouTube may be a site of ethnic-racial socialization where children develop prejudices against those of other races.

I hypothesize that time spent on YouTube and children’s observation of racial regularities should covary; as children spend more time on YouTube, they may observe more negatively valenced racial regularities including people of color [@guoharlow_2014_usergenerated; @rollinsetal_2022_who]. Thus, I hypothesize that if children spend more time on YouTube, they will display greater racial stereotyping and prejudice against outgroups. While some children may not be consciously aware of on-screen racial regularities, these dynamics may still affect their racial attitudes [@hugheswatford_2022_racial]. As such, I hypothesize that the relationship between children’s time spent on YouTube and their exhibited racial stereotyping and prejudice will be mediated by their observations of negative racial regularities.

One additional factor that may moderate the relationship between time spent on YouTube and racial attitudes is whether a child’s favorite YouTuber is of a race other than their own, via the parasocial contact hypothesis. This theory suggests that when individuals have limited real life interpersonal contact with minority groups, the formation of parasocial (one-sided) relationships with outgroup media figures may reduce stereotyping and prejudice [@schiappaetal_2005_parasocial; @wongetal_2022_theorizing]. Much of the parasocial contact hypothesis literature explores the prejudice reduction made possible by parasocial relationships with television characters, yet the growing popularity of social media presents another medium through which parasocial relationships may be formed. If positive parasocial contact hypothesis effects may be observed when individuals form relationships with characters in other media, so too should these effects be observed when individuals have parasocial relationships with outgroup influencers [@banasetal_2020_metaanalysis]. Thus, I pose my third hypothesis: the relationship between the amount of time that children spend on YouTube and their racial stereotyping and prejudice will be moderated by whether they have a parasocial relationship with a favorite YouTuber of a race other than their own. Specifically, if children have a favorite YouTuber of a race other than their own and they have a parasocial relationship with this YouTuber, they will display less racial stereotyping and prejudice.

@@

### Participants and Procedures {#sec-participants-and-procedures}
This study will include children between the ages of 8 and 13. Though children may express negative racial attitudes prior to this point in development, during early adolescence, children develop the ability to recognize and reflect on the racial patterns and dynamics present in their environments (Hughes & Watford, 2022). As such, this age range should allow me to observe how the observation racial regularities present on YouTube may affect children’s stereotyping and prejudicial attitudes, and how such a phenomenon develops. Participants will be recruited through Qualtrics Panels, which will allow me to obtain a representative sample of parents and children; other studies have used Qualtrics Panels with similar methods and populations (Byrd & Ahn, 2020).

Data will be collected during February and March of 2025 from families recruited via Qualtrics Panels. Participating families will receive two Qualtrics surveys to be completed asynchronously, and they will receive compensation (around $10-$15; the final amount will be determined by Qualtrics Panels) after both surveys have been completed. First, parents will complete a demographics and YouTube usage survey, in which they will answer questions related to parent and child demographics (child age, race/ethnicity, parent income and level of education, etc), as well as questions regarding their child’s YouTube usage (for instance, time spent on YouTube, as reported by their child’s device screen time). 
Then, children will complete their own survey.

@@

# BASED ON APAQUARTO DEMO - WILL CHANGE FOR FINAL; WANTED TO TEST RENDERING

# read in data
youtube <- read_csv("data/youtube.csv", col_names = TRUE)

@@

# BASED ON APAQUARTO DEMO - WILL CHANGE FOR FINAL; WANTED TO TEST RENDERING AND TRY INLINE REFERENCES
